### 2005-11-14 doc/EFA/efa.tex
*** empty log message ***

\begin{equation}
  g^{(A\|A')\|A''}(X^c) = \big[g(X) \wedge g'(X') \big] \wedge g''(X'') = g(X) \wedge \big[g'(X') \wedge g''(X'')] = g^{A\|(A'\|A'')}(X^c)
\end{equation}
\noindent Now consider the action function $a^{(A\|A')\|A''} : X^c
\rightarrow X^c$.
\newpage
\subsection{The translation of an EFA to  an FA}
To simplify the realization we shall restrict us to quite simple
action- and guard functions. For the updating functions we assume
that $a_{q \sigma}(x)=(a^1_{q \sigma}(x),...,a^n_{q
\sigma}(x))=(a^1_{q \sigma}(x_1),...,a^n_{q \sigma}(x_n))$. In
other words, the updating of the variables are independent from
each other. For the guard functions we assume that they are given
in disjunctive normal form $g_{q \sigma}(x)=g^1_{q \sigma}(x)\vee
...\vee g^j_{q \sigma}(x)$. We shall denote the number of
components $j$ in such an expression by $|g_{q \sigma}|$. These
assumptions makes it straight forward to translate an EFA to an
FA.

Given an extended finite automaton $A=\langle Q, \Sigma, \delta,
q_i, Q_m, X, G ,x_0, X_m \rangle$ with simple guard and action
functions, the algorithm can be divided into four steps:\\
- Form a regular FA, $A'$, from $A$ by removing $G$, $X$, $X_m$,
$x_0$ and change the names of all enabled events $\sigma$ to
$q\sigma$ (associate with the corresponding
state). Divide the event(transition) $q\sigma$ further into $|g_{q \sigma}|$ identical copies $\{(q\sigma)_k\}^{|g_{q \sigma}|}_{k=1}$.\\
- Realize an automata $A_{x_k}$ for each variable $x_k$, with
marked "states" $X_{mk}$,
 initial state $x_{k 0}$ and with as many events the total number of events of type $q\sigma$ in $A'$.\\
- Synchronize all automata.\\
- Change back to original event names.
\newpage
\subsection{Synchronous composition of EFA's with common variables}

>>>>

\begin{equation}
  g^{(A\|A')\|A''}(X^c) = \big[g(X) \wedge g'(X') \big] \wedge g''(X'') = g(X) \wedge \big[g'(X') \wedge g''(X'')] = g^{A\|(A'\|A'')}(X^c)
\end{equation}
\noindent Now consider the action function $a^{(A\|A')\|A''} : X^c
\rightarrow X^c$.
\newpage
\subsection{The translation of an EFA to  an FA}
To simplify the realization we shall restrict us to quite simple
action- and guard functions. For the updating functions we assume
that $a_{q \sigma}(x)=(a^1_{q \sigma}(x),...,a^n_{q
\sigma}(x))=(a^1_{q \sigma}(x_1),...,a^n_{q \sigma}(x_n))$. In
other words, the updating of the variables are independent from
each other. For the guard functions we assume that they are given
in disjunctive normal form $g_{q \sigma}(x)=g^1_{q \sigma}(x)\vee
...\vee g^j_{q \sigma}(x)$. We shall denote the number of "OR"
components $j$ in such an expression by $|g_{q \sigma}|$. These
assumptions makes it straight forward to translate an EFA to an
FA.

Given an extended finite automaton $A=\langle Q, \Sigma, \delta,
q_i, Q_m, X, G ,x_0, X_m \rangle$ with simple guard and action
functions, the algorithm can be divided into four steps:\\
- Form a regular FA, $A'$, from $A$ by removing $G$, $X$, $X_m$,
$x_0$ and change the names of all enabled events $\sigma$ to
$q\sigma$ (associate with the corresponding
state). Divide the event(transition) $q\sigma$ further into $|g_{q \sigma}|$ identical copies $\{(q\sigma)_k\}^{|g_{q \sigma}|}_{k=1}$.\\
- Realize an automata $A_{x_k}$ for each variable $x_k$, with
marked "states" $X_{mk}$,
 initial state $x_{k 0}$ and with as many events the total number of events of type $q\sigma$ in $A'$.\\
- Synchronize all automata $A_{x_k}$, $k=1,...,n$ and $A'$.\\
- Change back to original event names.
\newpage
\subsection{Synchronous composition of EFA's with common variables}
